### 2025-08-26 sections/4-results.tex
minor edits to results

In Figure~\ref{fig:results:scaling-plots}, we show how the throughput of each of CAKES's algorithms scales with cardinality for each of the six datasets we examined. To do this, we synthetically augmented the Fashion-MNIST, Glove-25, Sift, and Random datasets to create larger datasets using the process described in Section~\ref{sec:methods:synthetic-data}. For Silva and RadioML, due to the massive sizes of these datasets and challenges in generating plausible augmentations, we took random sub-samples ranging up to the entirety of the dataset---rather than augmented versions of the dataset---to examine how performance scales with cardinality.

@@

\textbf{General notes (applies to Tables \ref{tab:results:qps-and-recall-fmn},\ref{tab:results:qps-and-recall-glove}, \ref{tab:results:qps-and-recall-sift}).}
  Throughput is measured in queries per second. A recall value of $1.000*$ denotes imperfect recall that rounds to $1.000$. In each table, we observe that while recall for CAKES does \emph{not} degrade with cardinality, recall for
  HNSW and ANNOY degrades with cardinality. CAKES exhibits perfect recall on the Fashion-MNIST and Sift datasets, and near-perfect recall on the Glove-25 dataset (which uses cosine distance).

@@

\begin{table}
    \caption{Random dataset: throughput and recall.
    In contrast with the results on the ANN Benchmark datasets reported above, with the Random dataset, we observe that CAKES's algorithms perform quite slowly.CAKES exhibits perfect recall at all cardinalities, whereas HNSW and ANNOY exhibit \textit{much} lower recall on this random dataset than on any of the ANN benchmark datasets.
    }
    \label{tab:results:qps-and-recall-random}
    \small
    \setlength{\tabcolsep}{4pt}
    \begin{adjustbox}{width=\columnwidth,center}
    \begin{tabular}{@{} lcccccccc @{}}
    \toprule
    \textbf{Mult.} &
    \multicolumn{2}{c}{\textbf{HNSW}} &
    \multicolumn{2}{c}{\textbf{ANNOY}} &
    \multicolumn{2}{c}{\textbf{FAISS-IVF}} &
    \multicolumn{2}{c}{\textbf{CAKES}} \\
    \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}
        & QPS & Recall & QPS & Recall & QPS & Recall & QPS & Recall \\
        \midrule
        1  & \num{1.17e4} & 0.060 & \num{4.28e3} & 0.028 & \num{7.342} & 1.000* & \num{6.06e2} & 1.000 \\
        2  & \num{1.01e4} & 0.048 & \num{4.04e3} & 0.021 & \num{3.582} & 1.000* & \num{2.75e2} & 1.000 \\
        4  & \num{9.12e3} & 0.031 & \num{3.64e3} & 0.014 & \num{1.902} & 1.000* & \num{1.35e2} & 1.000 \\
        8  & \num{8.35e3} & 0.022 & \num{3.37e3} & 0.013 & \num{8.841} & 1.000* & \num{6.13e1} & 1.000 \\
        16 & \num{8.25e3} & 0.008 & \num{3.17e3} & 0.006 & \num{4.361} & 1.000* & \num{2.82e1} & 1.000 \\
        32 & --           & --    & \num{3.01e3} & 0.007 & \num{1.721} & 1.000* & \num{1.31e1} & 1.000 \\
        \bottomrule
    \end{tabular}
    \end{adjustbox}
    \end{table}

>>>>

In Figure~\ref{fig:results:scaling-plots}, we show how the throughput of each of CAKES's algorithms scales with cardinality for each of the six datasets we examined. To do this, we synthetically augmented the Fashion-MNIST, Glove-25, Sift, and Random datasets to create larger datasets using the process described in Section~\ref{sec:methods:synthetic-data}. For Silva and RadioML, due to the massive sizes of these datasets and challenges in generating plausible augmentations, we took random sub-samples ranging up to the entirety of the dataset---rather than augmented versions of the dataset---to examine how performance scales with cardinality. These plots also illustrate how the CAKES algorithms compare to na\"{i}ve linear search.

@@

  Throughput is measured in queries per second. A recall value of $1.000*$ denotes imperfect recall that rounds to $1.000$. In each of Tables \ref{tab:results:qps-and-recall-fmn},\ref{tab:results:qps-and-recall-glove}, \ref{tab:results:qps-and-recall-sift}, we observe that while recall for CAKES does \emph{not} degrade with cardinality, recall for
  HNSW and ANNOY does degrade with cardinality. CAKES exhibits perfect recall on the Fashion-MNIST and Sift datasets, and near-perfect recall on the Glove-25 dataset (which uses cosine distance).

@@

\begin{table}
    \caption{Random dataset: throughput and recall.
    In contrast with the results on the ANN Benchmark datasets reported above, with the Random dataset, we observe that CAKES's algorithms perform quite slowly. CAKES exhibits perfect recall at all cardinalities, whereas HNSW and ANNOY exhibit \textit{much} lower recall on this random dataset than on any of the ANN benchmark datasets.
    }
    \label{tab:results:qps-and-recall-random}
    \small
    \setlength{\tabcolsep}{4pt}
    \begin{adjustbox}{width=\columnwidth,center}
    \begin{tabular}{@{} lcccccccc @{}}
    \toprule
    \textbf{Mult.} &
    \multicolumn{2}{c}{\textbf{HNSW}} &
    \multicolumn{2}{c}{\textbf{ANNOY}} &
    \multicolumn{2}{c}{\textbf{FAISS-IVF}} &
    \multicolumn{2}{c}{\textbf{CAKES}} \\
    \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}
        & QPS & Recall & QPS & Recall & QPS & Recall & QPS & Recall \\
        \midrule
        1  & \num{1.17e4} & 0.060 & \num{4.28e3} & 0.028 & \num{7.342} & 1.000* & \num{6.06e2} & 1.000 \\
        2  & \num{1.01e4} & 0.048 & \num{4.04e3} & 0.021 & \num{3.582} & 1.000* & \num{2.75e2} & 1.000 \\
        4  & \num{9.12e3} & 0.031 & \num{3.64e3} & 0.014 & \num{1.902} & 1.000* & \num{1.35e2} & 1.000 \\
        8  & \num{8.35e3} & 0.022 & \num{3.37e3} & 0.013 & \num{8.841} & 1.000* & \num{6.13e1} & 1.000 \\
        16 & \num{8.25e3} & 0.008 & \num{3.17e3} & 0.006 & \num{4.361} & 1.000* & \num{2.82e1} & 1.000 \\
        32 & --           & --    & \num{3.01e3} & 0.007 & \num{1.721} & 1.000* & \num{1.31e1} & 1.000 \\
        \bottomrule
    \end{tabular}
    \end{adjustbox}
    \end{table}
